Project Protocol

### 2019-10-23 protocol.Rmd
table of investigators

|          Researcher          |    Role                    |    Affiliation                                                                |   |   |
|:----------------------------:|----------------------------|-------------------------------------------------------------------------------|---|---|
|    Stephanie Kobakian        |    Masters Student         | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Kerrie Mengersen    |    Principal Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Dr. Earl Duncan           |    Associate Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Dianne Cook         |    External Supervisor     |    Department of Econometrics and   Business Statistics, Monash University    |   |   |
|                              |                            |

>>>>

|          Researcher          |    Role                    |    Affiliation                                                                |   |   |
|:------------------------------------------|:--------------------------------------|:-------------------------------------------------------------------------------|---|---|
|    Stephanie Kobakian        |    Masters Student         | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Kerrie Mengersen    |    Principal Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Dr. Earl Duncan           |    Associate Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Dianne Cook         |    External Supervisor     |    Department of Econometrics and   Business Statistics, Monash University    |   |   |
